### 2024-07-28 mixed-models.qmd
20240728 - compare models

lmAndmixedModels <- list(
  "linearRegression" = pointsPerSeason_regressionModel,
  "randomIntercepts" = pointsPerSeason_randomIntercepts,
  "position" = pointsPerSeason_position,
  "fixedLinear" = pointsPerSeason_positionAgeFixedLinearSlopes,
  "randomLinear" = pointsPerSeason_positionAgeRandomLinearSlopes,
  "randomLinearFixedQuadratic" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  "randomLinearFixedQuadraticInteraction" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
)

@@

#AICcmodavg::aictab(lmAndmixedModels) # throws error (can't mix lm with lmer)
bbmle::AICtab(lmAndmixedModels)

AICcmodavg::aictab(mixedModels)
bbmle::AICtab(mixedModels)
```

@@

```{r}
BIC(
  pointsPerSeason_regressionModel,
  pointsPerSeason_randomIntercepts,
  pointsPerSeason_positionAgeFixedLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
  )
```

@@

###### Compare Models

@@

>>>>

lmAndMixedModels <- list(
  "linearRegression" = pointsPerSeason_regressionModel,
  "randomIntercepts" = pointsPerSeason_randomIntercepts,
  "position" = pointsPerSeason_position,
  "fixedLinear" = pointsPerSeason_positionAgeFixedLinearSlopes,
  "randomLinear" = pointsPerSeason_positionAgeRandomLinearSlopes,
  "randomLinearFixedQuadratic" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  "randomLinearFixedQuadraticInteraction" = pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
)

@@

bbmle::AICtab(lmAndMixedModels)
```

@@

```{r}
BIC(
  pointsPerSeason_regressionModel,
  pointsPerSeason_randomIntercepts,
  pointsPerSeason_positionAgeFixedLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopes,
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteraction
  )

#AICcmodavg::bictab(lmAndMixedModels) # throws error (can't mix lm with lmer)
bbmle::BICtab(lmVsMixedModel)

AICcmodavg::bictab(mixedModels) # throws error (can't mix lm with lmer)
#bbmle::AICctab(mixedModels) # throws error (different numbers of observations)

AICcmodavg::bictab(mixedModels1)
bbmle::BICtab(mixedModels1)

AICcmodavg::bictab(mixedModels2)
bbmle::BICtab(mixedModels2)
```

@@

###### Compare Models {#sec-fantasyPointsByAgeExperienceModelsAgeGAMcompare}

@@

#AICcmodavg::bictab(linearMixedModelsVsGAM) # throws error (can't mix bam with lmer)
bbmle::BICtab(linearMixedModelsVsGAM)
